### 2024-03-29 doc/sections/introduction.tex
[ tex ] Make a submittable version

We present an algebraic semantics and semantic proof of cut-elimination for the multiplicative-additive system MAV~\cite{Horne15:mav}, which extends the basic system BV\footnote{
      BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pairwise production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
}~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}.
The proof is constructive and mechanised in Agda~\cite{Agda264}.

>>>>

We present an algebraic semantics and semantic proof of generalised cut-elimination for the multiplicative-additive system MAV~\cite{Horne15:mav}, which extends the basic system BV\footnote{
      BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pairwise production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
}~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}.
The proof is constructive and mechanised in Agda~\cite{Agda264}.

### 2024-03-29 doc/sections/mav-mechanisation.tex
[ tex ] Make a submittable version

The formalisation uses setoids to represent sets, reusing definitions
from the Agda Standard Library \cite{AgdaStdlib20}. Each of the
definitions and propositions above links to the corresponding part of
the development.

As well as giving confidence in our results, a key benefit of
formalising the development in a proof assistant like Agda is that the
proof normalisation process (\Cref{thm:cut-elim}) is
executable. For example, we can normalise the one step SMAV proof
using \cref{rule:Axiom} of $\vP \vParr \vDual{\vP}$ where
$\vP = (\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit)$ to a FIXME
step MAV proof, given in the Appendix.

\bob{Wen: do you want to write something about the formalisation of
  the congruence rules in the proof system?}

>>>>

The formalisation uses setoids to represent sets, reusing definitions
from the Agda Standard Library \cite{AgdaStdlib20}.
% Each of the
% definitions and propositions above links to the corresponding part of
% the development.

We did not attempt to formalise the syntactic proof of generalised
cut-elimination directly. We suspect that this would likely be
extremely involved due to the widespread and implicit use of syntactic
equalties when manipulating formulas, as well as the construction of
the relevant termination measures. The semantic constructions are
relatively straightforward to formalise in Agda.

As well as giving confidence in our results, a key benefit of
formalising the development in a proof assistant like Agda is that the
proof normalisation process (\Cref{thm:cut-elim}) is executable. For
example, we can normalise the one step SMAV proof using
\cref{rule:Axiom} of $\vP \vParr \vDual{\vP}$ where
$\vP = (\vUnit \vPlus \vUnit) \vSeq (\vUnit \vWith \vUnit)$ to a 38
step (of which 9 are $\vInferFrom$ steps) MAV proof, presented online
here:
\begin{center}
  \url{https://bobatkey.github.io/semantic-cut-elimination/MAV.Example.html#908}
\end{center}

% \bob{Wen: do you want to write something about the formalisation of
%   the congruence rules in the proof system?}

### 2024-03-29 doc/sections/mav-syntax.tex
[ tex ] Make a submittable version

Duality ($\vDual\vP$) is an involutive function on structures that obeys the De Morgan laws for the multiplicative and additive connectives and preserves the self-dual connective seq.

@@

Structures are considered equivalent modulo the decidable equality $\vEquiv$, which is the smallest congruence defined by the associativity, commutativity, and identity laws that ensure that $(\vSeq,\vUnit)$ forms a monoid, and $(\vTens,\vUnit)$ and $(\vParr,\vUnit)$ form commutative monoids.

>>>>

Duality ($\vDual\vP$) is an involutive function on structures that obeys the De Morgan laws for the multiplicative and additive connectives and preserves the self-dual connective $\vSeq$.

@@

Structures are considered equivalent modulo the equality $\vEquiv$, which is the smallest congruence defined by the associativity, commutativity, and identity laws that ensure that $(\vSeq,\vUnit)$ forms a monoid, and $(\vTens,\vUnit)$ and $(\vParr,\vUnit)$ form commutative monoids.
